From noise to knowledge: how randomness generates novel phenomena and information

### 2017-06-14 paper.Rmd
update sketch

---
title: "Noise-induced phenonema in Population Biology"
author: "Carl Boettiger"
---

Outline

@@

## Noise-induced phenonema

@@

## Noise as information

>>>>

---
title: "From noise to knowledge: how randomness generates novel phenomena and information"
author: "Carl Boettiger"
---

# Outline

In this paper, I provide a brief synthesis of ecological research in stochastic phenomena. Noise, as the term itself suggests, is most often seen a nuisance to ecological insight, a inconvenient reality that must be acknowledged, a haystack that must be stripped away to reveal the processes of interest underneath. Yet despite this well-earned reputation, noise is often interesting in its own right: noise can induce novel phenomena that could not be understood from some underlying determinstic model alone.  Nor is all noise the same, and close examination of differences in in frequency, color or magnitude can reveal insights that would otherwise be inaccessible.  While an exhaustive review is beyond the scope of this piece, I endeavor to highlight some of the most interesting examples of both noise-induced phenomena and noise-derived information, and point the way towards yet uncharted territory.

@@

## Noise the nuisance: Noise can obscure patterns

- deterministic skeletons, signal-to-noise ratio, model fitting

## Noise the creator: Noise can induced novel phenonema

@@

## Noise the informer: Noise can provide novel information
